CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-11 README.Rmd
Update README with statement of need.

---
output: github_document
bibliography: References.bib
---

@@

This repository contains a paper submitted to 
the [Journal of Open Source Software (JOSS)](https://joss.theoj.org)
covering the suite of `R` packages associated with the 
CL-PFU database^["CL-PFU" 
is an initialism for "Country-Level
Primary, Final, and Useful."
The CL-PFU database contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames
stored as [pins][link-pins] on a pinboard, 
not SQL or similar databases.].

@@

We created a suite of `R` packages 
to support the creation and use of the CL-PFU database.
The CL-PFU database is a new resouce 
for the Societal Exergy Analysis (SEA) research community and
assists SEA practitioners 
to analyze energy conversion chains (ECCs).
The new packages enable, for the first time, scalable SEA.

>>>>

---
output: github_document
bibliography: paper.bib
---

@@

This repository contains a paper submitted to 
the [Journal of Open Source Software (JOSS)](https://joss.theoj.org)
covering the suite of `R` packages associated with the 
CL-PFU^["CL-PFU" 
is an initialism for "Country-Level
Primary, Final, and Useful."
The CL-PFU database contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames
stored as [pins][link-pins] on a pinboard, 
not SQL or similar databases.] database.

## Statement of need

Historically, Societal Exergy Analysis (SEA)
practitioners have analyzed the ECCs
of individual countries using linked spreadsheets,
often starting with primary- and final-stage data 
from the [International Energy Agency][link-iea]'s (IEA's)
[extended world energy balances][link-ieaeweb] (EWEBs)
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa]. 
Data were stored in varying and inconsistent formats.
An early SEA database [@De-Stercke:2014]
estimated energy efficiencies 
of end-use machines using the economic status of countries,
thereby precluding use in energy-economy studies.

The authors of the current paper and others in the field
wanted to expand SEA to cover all countries, but
the spreadsheet approach to SEA was
deemed not scalable.
A new approach to SEA was needed, 
one that scaled across all countries 
for many years without relying on economic data
to estimate machine efficiencies.

@@

We created a suite of `R` packages 
to support the creation and use of the CL-PFU database.
The CL-PFU database is a new resouce 
for the SEA research community and
assists SEA practitioners 
to analyze energy conversion chains (ECCs).
The new packages enable, for the first time, scalable SEA.
